\cvsection{Professional experience}

	\begin{cventries}
	
		\cventry
			{Software Engineer (Android \& Data)}
			{\href{https://www.picnic.nl}{Picnic Supermarkt}}
			{Amsterdam, The Netherlands}
			{Sep. 2015 - Sep. 2017}
			{
				\begin{cvitems}
					\item Enhanced the Android development cycle by setting up CI \& moving to a clean architecture.
					\item Helped to reach 100 000 daily active users with 99.8\% crash free sessions.
					\item Managed migration of a custom analytics pipeline to \textit{Snowplow Analytics}.
					\item Improved and stabilized performances of daily data mart generation.
					\item Developed \textit{Spark} jobs to help Picnic grow its data-driven culture.
					\item Created internal tools and APIs to guarantee data consistency and scalability.
				\end{cvitems}
			}
		
		\cventry
			{Software engineer (Android)}
			{\href{https://www.dashlane.com}{Dashlane}}
			{Paris, France}
			{Feb. 2013 - Sep. 2015}
			{
				\begin{cvitems}
					\item Involved at every project phase, from conception to app store deployment.
					\item Used \textit{Java} and \textit{C++} (combined with \textit{JNI}) to build one of the top productivity app.
					\item Helped to reach more than 1 000 000 downloads on Google Play.
				\end{cvitems}
			}
		
		\cventry
			{Intern (Android developer)}
			{\href{https://www.photoservice.com}{CGIN}}
			{Mérignac, France}
			{Jun. - Aug. 2012}
			{
				\begin{cvitems}
					\item Successfully ported the \textit{iOS} application to \textit{Android}.
					\item Involved in full product life cycle from design and development to deployment.
					\item Used \textit{Java} and \textit{C++} (using \textit{JNI} and \textit{OpenCV}) to perform intensive image processing.
				\end{cvitems}
			}
		
		\cventry
			{Intern (Web developer)}
			{\href{https://openflyers.com/}{Openflyers}}
			{Le Bouscat, France}
			{Jul. - Aug. 2011}
			{
				\begin{cvitems}
					\item Adapted Openflyers' framework to JQuery.
					\item Successfully developed a new functionality to dynamically edit data of various charts, using AJAX, PHP and SQL.
				\end{cvitems}
			}
		
		\cventry
			{Intern (Web developer)}
			{\href{https://www.logitourisme.com/}{Logitourisme}}
			{Courbouzon, France}
			{May - Aug. 2010}
			{
				\begin{cvitems}
					\item Succeed in programming a Content Management System using PHP, MySQL and JQuery.
					\item In charge of the first deployment of Logi-D. 
				\end{cvitems}
			}
	
	\end{cventries}